Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Expand section on final considerations.

To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.

The instantaneous profile yields higher cooling capacity, even by
reducing the blow fraction on rectified cosine, up to levels achieved by pumping and valving systems, mainly restricted by valve opening times

The ramp profile is a feasible approximation for the instantaneous
profile, and can be optimized for increasing cooling capacity.
In particular, by synchronizing the plateau durations between fluid
and magnetic profiles.

>>>>

To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way. The instantaneous, rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with regenerator geometric parameters. These waveforms can be found in existing MR devices published in the literature.

Using a simplified model, the instantaneous profile yields higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times. This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of MR systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration.

The ramp profile is a feasible approximation for the instantaneous
profile without abrupt changes in the magnetic field plateaus. This waveform can be optimized for increasing cooling capacity, in particular by synchronizing the plateau durations between fluid and magnetic profiles.
